Study locations

### 2022-12-17 Scripts/Map_study_locations.Rmd
Adding STEP datasets

colors <- c("#8AD69E", "#74C5CE",  "#FDE9DE", "#45A631", "#95F7F0", "#CB53E1",
            "#FE90BB", "#B187E1", "#F8A982", "#0075DC", 
            "#993F00",  "#5EF1F2", "#005C31", "#74C5CE", "black", "lightblue",  "darkorange3","#8F7C00",
            "#8F7C00","#8F7C00", "#9DCC00", "#C20088", "gold1","#FFA8BB","#426600","#94FFB5","#003380",  
            "#FF0010","#FF0010", "salmon", "seashell3","greenyellow","mediumaquamarine")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)

>>>>

colors <- c("#8AD69E", "#74C5CE",  "#FDE9DE",  "#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)
